---
title: Observer analyses (Supplemental Material)
author: Hannah, 2/19/2019
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(width=140)
require(dplyr)
require(tidyr)
require(ggplot2)
require(lme4)
require(lmerTest)
require(knitr)
require(reshape2)
require(kableExtra)

```
### Includes analyses regarding observer, IMS, and EMS that are included in SM.

**Subject exclusions match manuscript.**

Data for Study 1 was collected in Fall 2015. Data for Study 2 was collected in Fall 2016.

**In Study 1:**  
- 101 subjects participated  
- 8 subjects' AP data was discarded (see "Study1_badsubsAP.txt")  
- 9 subjects' WIT data was discarded (see "Study1_badsubsWIT.txt")    
*This left 93 subjects with AP data and 92 subjects with WIT data.*

Additionally, IMS/EMS data is missing for subs 3, 27, 53, 82, 88, 89, 90, and 101. 

**In Study 2:**  
- 206 subjects participated  
- 8 subjects' AP data was discarded (see "Study2_badsubsAP.txt")  
- 7 subjects' WIT data was discarded (see "Study2_badsubsWIT.txt")  
*This left 198 subjects with AP data and 199 subjects with WIT data.*

Additionally, IMS/EMS data is missing for 111, 189, and 201.

There were 48 trials for each condition in each task (192 trials total for each task). In Study 2, each task was split into two sections so that participants could answer anxiety questions in the middle and end of each task.


### Study 1: 
Task is effect coded (APT = -1, WIT = 1). IMS and EMS are both standardized.  

An IMS-EMS difference score was created to approximate the degree to which motiviation to be unbiased is internalized. A higher IMS-EMS difference score represents more internalization.  
``` {r}
# PDP estimates
s1.PDP.APT = read.delim("Study1_pdpEstimates_APT.txt")
s1.PDP.WIT = read.delim("Study1_pdpEstimates_WIT.txt")


# take out bad subs
s1.bs.APT = read.delim("Study1_badSubsAP.txt")
s1.bs.WIT = read.delim("Study1_badSubsWIT.txt")

s1.PDP.APT = s1.PDP.APT[!(s1.PDP.APT$Subject %in% s1.bs.WIT$Subject) & !(s1.PDP.APT$Subject %in% s1.bs.APT$Subject),]
s1.PDP.WIT = s1.PDP.WIT[!(s1.PDP.WIT$Subject %in% s1.bs.WIT$Subject) & !(s1.PDP.WIT$Subject %in% s1.bs.APT$Subject),]

# Add standarized estimates (depends on subjects included)
s1.PDP.APT$Cmean.scale = scale(s1.PDP.APT$C_mean)
s1.PDP.WIT$Cmean.scale = scale(s1.PDP.WIT$C_mean)
s1.PDP.APT$AResid.scale = scale(s1.PDP.APT$AResid)
s1.PDP.WIT$AResid.scale = scale(s1.PDP.WIT$AResid)

# C estimates
s1.est = rbind(select(s1.PDP.APT, Task, Subject, IMS, EMS, Observer, Cmean.scale, AResid.scale),
               select(s1.PDP.WIT, Task, Subject, IMS, EMS, Observer, Cmean.scale, AResid.scale))

# Effect code task
s1.est$Task.e = -1
s1.est$Task.e[s1.est$Task == "WIT"] = 1

# add IMS-EMS diff score
s1.est$IMSEMS.diff = s1.est$IMS-s1.est$EMS

# C estimates
# Observer x Task
C1 = lmer(Cmean.scale ~ Observer*Task.e + (1|Subject), data = s1.est) %>% 
  summary()
# IMS x Task
C2 = lmer(Cmean.scale ~ scale(IMS)*Task.e + (1|Subject), data = s1.est) %>% 
  summary()
# EMS x Task
C3 = lmer(Cmean.scale ~ scale(EMS)*Task.e + (1|Subject), data = s1.est) %>% 
  summary()
# IMS-EMS x Task
C4 = lmer(Cmean.scale ~ scale(IMSEMS.diff)*Task.e + (1|Subject), data = s1.est) %>% 
  summary()

# A estimates
# Observer x Task
A1 = lmer(AResid.scale ~ Observer*Task.e + (1|Subject), data = s1.est) %>% 
  summary()
# IMS x Task
A2 = lmer(AResid.scale ~ scale(IMS)*Task.e + (1|Subject), data = s1.est) %>% 
  summary()
# EMS x Task
A3 = lmer(AResid.scale ~ scale(EMS)*Task.e + (1|Subject), data = s1.est) %>% 
  summary()
# IMS-EMS x Task
A4 = lmer(AResid.scale ~ scale(IMSEMS.diff)*Task.e + (1|Subject), data = s1.est) %>% 
  summary()
```

#### Observer x Task on PDP-C estimates  
``` {r}
table = round(C1$coefficients, digits=3) # need to keep table as an object for row_spec()
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### IMS x Task on PDP-C estimates  
``` {r}
table = round(C2$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### EMS x Task on PDP-C estimates  
``` {r}
table = round(C3$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### IMS-EMS x Task on PDP-C estimates  
``` {r}
table = round(C4$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### Observer x Task on PDP-A estimates  
``` {r}
table = round(A1$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### IMS x Task on PDP-A estimates  
``` {r}
table = round(A2$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### EMS x Task on PDP-A estimates  
``` {r}
table = round(A3$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### IMS-EMS x Task on PDP-A estimates  
``` {r}
table = round(A4$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```


### Study 2: 
Task is effect coded (APT = -1, WIT = 1). IMS and EMS are both standardized.  

An IMS-EMS difference score was created to approximate the degree to which motiviation to be unbiased is internalized. A higher IMS-EMS difference score represents more internalization.  
``` {r}
# PDP estimates
s2.PDP.APT = read.delim("Study2_pdpEstimates_APT.txt")
s2.PDP.WIT = read.delim("Study2_pdpEstimates_WIT.txt")

# take out bad subs
s2.bs.APT = read.delim("Study2_badSubsAP.txt")
s2.bs.WIT = read.delim("Study2_badSubsWIT.txt")

s2.PDP.APT = s2.PDP.APT[!(s2.PDP.APT$Subject %in% s2.bs.WIT$Subject) & !(s2.PDP.APT$Subject %in% s2.bs.APT$Subject),]
s2.PDP.WIT = s2.PDP.WIT[!(s2.PDP.WIT$Subject %in% s2.bs.WIT$Subject) & !(s2.PDP.WIT$Subject %in% s2.bs.APT$Subject),]

# Add standarized estimates (depends on subjects included)
s2.PDP.APT$Cmean.scale = scale(s2.PDP.APT$C_mean)
s2.PDP.WIT$Cmean.scale = scale(s2.PDP.WIT$C_mean)
s2.PDP.APT$AResid.scale = scale(s2.PDP.APT$AResid)
s2.PDP.WIT$AResid.scale = scale(s2.PDP.WIT$AResid)

# C estimates
s2.est = rbind(select(s2.PDP.APT, Task, Subject, IMS, EMS, Observer, Cmean.scale, AResid.scale),
               select(s2.PDP.WIT, Task, Subject, IMS, EMS, Observer, Cmean.scale, AResid.scale))

# Effect code task
s2.est$Task.e = -1
s2.est$Task.e[s2.est$Task == "WIT"] = 1

# add IMS-EMS diff score
s2.est$IMSEMS.diff = s2.est$IMS-s2.est$EMS

# C estimates
# Observer x Task
C1 = lmer(Cmean.scale ~ Observer*Task.e + (1|Subject), data = s2.est) %>% 
  summary()
# IMS x Task
C2 = lmer(Cmean.scale ~ scale(IMS)*Task.e + (1|Subject), data = s2.est) %>% 
  summary()
# EMS x Task
C3 = lmer(Cmean.scale ~ scale(EMS)*Task.e + (1|Subject), data = s2.est) %>% 
  summary()
# IMS-EMS x Task
C4 = lmer(Cmean.scale ~ scale(IMSEMS.diff)*Task.e + (1|Subject), data = s2.est) %>% 
  summary()

# A estimates
# Observer x Task
A1 = lmer(AResid.scale ~ Observer*Task.e + (1|Subject), data = s2.est) %>% 
  summary()
# IMS x Task
A2 = lmer(AResid.scale ~ scale(IMS)*Task.e + (1|Subject), data = s2.est) %>% 
  summary()
# EMS x Task
A3 = lmer(AResid.scale ~ scale(EMS)*Task.e + (1|Subject), data = s2.est) %>% 
  summary()
# IMS-EMS x Task
A4 = lmer(AResid.scale ~ scale(IMSEMS.diff)*Task.e + (1|Subject), data = s2.est) %>% 
  summary()
```

#### Observer x Task on PDP-C estimates  
``` {r}
table = round(C1$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### IMS x Task on PDP-C estimates  
``` {r}
table = round(C2$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### EMS x Task on PDP-C estimates  
``` {r}
table = round(C3$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### IMS-EMS x Task on PDP-C estimates  
``` {r}
table = round(C4$coefficients, digits=3) 
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### Observer x Task on PDP-A estimates  
``` {r}
table = round(A1$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### IMS x Task on PDP-A estimates  
``` {r}
table = round(A2$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### EMS x Task on PDP-A estimates  
``` {r}
table = round(A3$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

#### IMS-EMS x Task on PDP-A estimates  
``` {r}
table = round(A4$coefficients, digits=3)
kable(table) %>% 
  kable_styling(full_width = F, position = "center") %>% 
  row_spec(which(table[,5] < .05), bold = T, background = "#FFFF66")
```

