---
title: Observer analyses
author: Hannah, 2/19/2019
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(width=140)
require(dplyr)
require(tidyr)
require(ggplot2)
require(lme4)
require(lmerTest)
require(knitr)
require(reshape2)
```

### Original subject exclusions

Data for Study 1 was collected in Fall 2015. Data for Study 2 was collected in Fall 2016.

**In Study 1:**  
- 101 subjects participated  
- 8 subjects' AP data was discarded (see "Study1_badsubsAP.txt")  
- 9 subjects' WIT data was discarded (see "Study1_badsubsWIT.txt")    
*This left 93 subjects with AP data and 92 subjects with WIT data.*

Additionally, IMS/EMS data is missing for subs 3, 27, 53, 82, 88, 89, 90, and 101. 

**In Study 2:**  
- 206 subjects participated  
- 8 subjects' AP data was discarded (see "Study2_badsubsAP.txt")  
- 7 subjects' WIT data was discarded (see "Study2_badsubsWIT.txt")  
*This left 198 subjects with AP data and 199 subjects with WIT data.*

Additionally, IMS/EMS data is missing for 111, 189, and 201.

There were 48 trials for each condition in each task (192 trials total for each task). In Study 2, each task was split into two sections so that participants could answer anxiety questions in the middle and end of each task.

### 1. Accuracy in each task:  
#### 2 (Prime: Black/White) x 2 (Target: gun/tool or positive/negative) rANOVA  
Only showing interaction indicating racial bias (Prime x Target). For calculation of effect sizes, see "7 Effect sizes.R"  
#### Study 1:  
**WIT**  
```{r data, echo = FALSE}
# For analyses with accuracy as DV, need trials to be grouped into conditions (ie number of errors in each condition)
s1.acc = read.delim("Study1_accuracy.txt")

# separate by task
s1.acc.APT = s1.acc[s1.acc$Task == "APT",]
s1.acc.WIT = s1.acc[s1.acc$Task == "WIT",]

# remove bad subs
s1.bs.APT = read.delim("Study1_badSubsAP.txt")
s1.acc.APT = s1.acc.APT[!(s1.acc.APT$Subject %in% s1.bs.APT$Subject),]

s1.bs.WIT = read.delim("Study1_badSubsWIT.txt")
s1.acc.WIT = s1.acc.WIT[!(s1.acc.WIT$Subject %in% s1.bs.WIT$Subject),]

s1.acc.APT$Subject = factor(s1.acc.APT$Subject)
s1.acc.WIT$Subject = factor(s1.acc.WIT$Subject)

# Race x Valence on accuracy (WIT)
sum = aov(Accuracy ~ PrimeType*TargetType + Error(Subject/(PrimeType*TargetType)), data = s1.acc.WIT) %>% 
  summary()

sum$`Error: Subject:PrimeType:TargetType`


```

**AP**
``` {r AP, echo = FALSE}
# Race x Valence on accuracy (WIT)
sum = aov(Accuracy ~ PrimeType*TargetType + Error(Subject/(PrimeType*TargetType)), data = s1.acc.APT) %>% 
  summary()

sum$`Error: Subject:PrimeType:TargetType`
```


#### Study 2: 
Only showing interaction indicating racial bias (Prime x Target). For calculation of effect sizes, see "7 Effect sizes.R"  
**WIT**  
```{r data2, echo = FALSE}
s2.acc = read.delim("Study2_accuracy.txt")

# separate by task
s2.acc.APT = s2.acc[s2.acc$Task == "APT",]
s2.acc.WIT = s2.acc[s2.acc$Task == "WIT",]

# remove bad subs
s2.bs.APT = read.delim("Study2_badSubsAP.txt")
s2.acc.APT = s2.acc.APT[!(s2.acc.APT$Subject %in% s2.bs.APT$Subject),]

s2.bs.WIT = read.delim("Study2_badSubsWIT.txt")
s2.acc.WIT = s2.acc.WIT[!(s2.acc.WIT$Subject %in% s2.bs.WIT$Subject),]

s2.acc.APT$Subject = factor(s2.acc.APT$Subject)
s2.acc.WIT$Subject = factor(s2.acc.WIT$Subject)

# Race x Valence on accuracy (WIT)
sum = aov(Accuracy ~ PrimeType*TargetType + Error(Subject/(PrimeType*TargetType)), data = s2.acc.WIT) %>% 
  summary()

sum$`Error: Subject:PrimeType:TargetType`
```

**AP**
``` {r AP2, echo = FALSE}
# Race x Valence on accuracy (WIT)
sum = aov(Accuracy ~ PrimeType*TargetType + Error(Subject/(PrimeType*TargetType)), data = s2.acc.APT) %>% 
  summary()

sum$`Error: Subject:PrimeType:TargetType`
```

### 2. Comparing accuracy across tasks

#### Study 1
Excludes subjects that don't have data in both tasks (only includes sample of 90).  

#### A. Correlation between performance bias scores on each task
``` {r perfBias.s1, echo=F, warning=F}
s1.perfBias = read.delim("Study1_perfBias.txt")

# take out bs for both APT and WIT
s1.perfBias = s1.perfBias[!(s1.perfBias$Subject %in% s1.bs.APT$Subject),]
s1.perfBias = s1.perfBias[!(s1.perfBias$Subject %in% s1.bs.WIT$Subject),]

# standardize perfBias estimates (depends on who is included in the sample, so needs to be done after subs are excluded)
s1.perfBias$WITStand = scale(s1.perfBias$WITperfBias)
s1.perfBias$APStand = scale(s1.perfBias$APperfBias)

# Look at correlation between tasks
ggplot(s1.perfBias, aes(APStand, WITStand)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "Stand. Performance bias on AP", y = "Stand. Performance bias on WIT") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(APStand ~ WITStand, data = s1.perfBias) %>%
  summary()
```

#### B. Examine 3 way Prime x Target x Task interaction  
``` {r 3way.s1, echo=F, wanring=F}
# Look just at subjects that have data for both tasks, otherwise throws error ("Error() model is singular")
# Probably because some subjects don't have data across both levels of task
s1.acc.nobs = s1.acc[!(s1.acc$Subject %in% s1.bs.WIT$Subject) & !(s1.acc$Subject %in% s1.bs.AP$Subject),]
s1.acc.nobs$Subject = factor(s1.acc.nobs$Subject)

# Total number of errors (looking at three-way interaction)
facet_labels <- c(AP = "APT", WIT = "WIT")

# Figure 1 ----------------------------------------------------------------
ggplot(s1.acc.nobs, aes(PrimeType, Accuracy, fill = ConType)) +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .2) +
  facet_wrap(~Task, labeller=labeller(Task = facet_labels)) + 
  #  ggtitle("Total number of errors") +
  labs(y = "Accuracy rate", x = "Race of Prime") +
  scale_fill_manual(values=c("black","grey70"), guide = guide_legend(title = NULL)) +
  theme_bw() +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        strip.text.x = element_text(face = "bold", size = 14),
        strip.background = element_rect(fill = "grey98"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

ggsave("./Figures/Accuracy_Study1.tiff")


# See if pattern of racial bias differs across two tasks- TOTAL ERRORS
sum2 = aov(Accuracy ~ (PrimeType*ConType*Task)+Error(Subject/(PrimeType*ConType*Task)), data = s1.acc.nobs) %>%
  summary()

sum2$`Error: Subject:PrimeType:ConType:Task`

```

``` {r, echo = F, eval=F}
# check correlation between conditions for sensitivity power analysis
wide = spread(select(s1.acc.nobs, Subject, TrialType, Accuracy), TrialType, Accuracy)

rs = cor(select(wide, -Subject))
```

#### Study 2
Excludes subjects that don't have data in both tasks (only includes sample of 195).  

#### A. Correlation between performance bias scores on each task
``` {r perfBias.s2, echo=F, warning=F}
s2.perfBias = read.delim("Study2_perfBias.txt")

# take out bs for both APT and WIT
s2.perfBias = s2.perfBias[!(s2.perfBias$Subject %in% s2.bs.APT$Subject),]
s2.perfBias = s2.perfBias[!(s2.perfBias$Subject %in% s2.bs.WIT$Subject),]

# standardize perfBias estimates (depends on who is included in the sample, so needs to be done after subs are excluded)
s2.perfBias$WITStand = scale(s2.perfBias$WITperfBias)
s2.perfBias$APStand = scale(s2.perfBias$APperfBias)

# Look at correlation between tasks
ggplot(s2.perfBias, aes(APStand, WITStand)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "Stand. Performance bias on AP", y = "Stand. Performance bias on WIT") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(APStand ~ WITStand, data = s2.perfBias) %>%
  summary()
```

#### B. Examine 3 way Prime x Target x Task interaction  
``` {r 3way.s2, echo=F, wanring=F}
# Look just at subjects that have data for both tasks, otherwise throws error ("Error() model is singular")
# Probably because some subjects don't have data across both levels of task
s2.acc.nobs = s2.acc[!(s2.acc$Subject %in% s2.bs.WIT$Subject) & !(s2.acc$Subject %in% s2.bs.APT$Subject),]
s2.acc.nobs$Subject = factor(s2.acc.nobs$Subject)

# Total number of errors (looking at three-way interaction)
facet_labels <- c(AP = "APT", WIT = "WIT")

# Figure 1 ----------------------------------------------------------------
ggplot(s2.acc.nobs, aes(PrimeType, Accuracy, fill = ConType)) +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .2) +
  facet_wrap(~Task, labeller=labeller(Task = facet_labels)) + 
  #  ggtitle("Total number of errors") +
  labs(y = "Accuracy rate", x = "Race of Prime") +
  scale_fill_manual(values=c("black","grey70"), guide = guide_legend(title = NULL)) +
  theme_bw() +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        strip.text.x = element_text(face = "bold", size = 14),
        strip.background = element_rect(fill = "grey98"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

ggsave("./Figures/Accuracy_Study2.tiff")


# See if pattern of racial bias differs across two tasks- TOTAL ERRORS
sum2 = aov(Accuracy ~ (PrimeType*ConType*Task)+Error(Subject/(PrimeType*ConType*Task)), data = s2.acc.nobs) %>%
  summary()

sum2$`Error: Subject:PrimeType:ConType:Task`

```

### 3. Correspondance in PDP estimates across tasks  
Only includes data for participants with data in both tasks (N = 90).  

####Study 1:  
``` {r correl, echo=F}

## CHANGES TO PDP ESTIMATE CALCULATION SINCE INTIIAL SUBMISSION:
# 1. TOOK OUT MISS TRIALS (IE ONLY INCLUDED TRIALS IN WHICH A RESPONSE WAS RECORDED WITHIN THE TIME WINDOW)
# 2. REPLACED NEGATIVE ESTIMATES WITH TRIALS

# compare PDP-C estimates across tasks
s1.PDP.APT = read.delim("Study1_pdpEstimates_APT.txt")
s1.PDP.WIT = read.delim("Study1_pdpEstimates_WIT.txt")

# take out subs with missing data
s1.PDP.APT = s1.PDP.APT[!(s1.PDP.APT$Subject %in% s1.bs.WIT$Subject) & !(s1.PDP.APT$Subject %in% s1.bs.APT$Subject),]

s1.PDP.WIT = s1.PDP.WIT[!(s1.PDP.WIT$Subject %in% s1.bs.WIT$Subject) & !(s1.PDP.WIT$Subject %in% s1.bs.APT$Subject),]

# Add standarized estimates (depends on subjects included)
s1.PDP.APT$Cmean.scale = scale(s1.PDP.APT$C_mean)
s1.PDP.WIT$Cmean.scale = scale(s1.PDP.WIT$C_mean)
s1.PDP.APT$AResid.scale = scale(s1.PDP.APT$AResid)
s1.PDP.WIT$AResid.scale = scale(s1.PDP.WIT$AResid)

# ## COMPARISON BETWEEN PDP ESTIMATES FROM INITIAL SUBMISSION AND CHANGED PDP ESTIMATES
# s1.widePDP = read.delim("Old/Study1_PDP_wide.txt")
# # APT C ESTIMATES: r = .97
# cor(s1.widePDP$APT_MeanC, s1.PDP.APT$C_mean)
# ggsave("./Compare new and old PDP est/Study1_APT_Cmean.jpg", 
#        qplot(s1.widePDP$APT_MeanC, s1.PDP.APT$C_mean, 
#              xlab = "Old PDP-C", ylab = "New PDP-C", main = "APT"))
# # APT A ESTIMATES: r = .82
# cor(s1.widePDP$APT_AResid, s1.PDP.APT$AResid)
# ggsave("./Compare new and old PDP est/Study1_APT_AResid.jpg", 
#        qplot(s1.widePDP$APT_AResid, s1.PDP.APT$AResid, 
#              xlab = "Old PDP-A", ylab = "New PDP-A", main = "APT"))
# # WIT C ESTIMATES: r = .97
# cor(s1.widePDP$WIT_MeanC, s1.PDP.WIT$C_mean)
# ggsave("./Compare new and old PDP est/Study1_WIT_Cmean.jpg", 
#        qplot(s1.widePDP$WIT_MeanC, s1.PDP.WIT$C_mean, 
#              xlab = "Old PDP-C", ylab = "New PDP-C", main = "WIT"))
# # WIT A ESTIMATES: r = .67
# cor(s1.widePDP$WIT_AResid, s1.PDP.WIT$AResid)
# ggsave("./Compare new and old PDP est/Study1_WIT_AResid.jpg", 
#        qplot(s1.widePDP$WIT_AResid, s1.PDP.WIT$AResid, 
#              xlab = "Old PDP-A", ylab = "New PDP-A", main = "WIT"))

# C estimates
s1.Cest = 
  cbind(rename(s1.PDP.APT, APT.Cmean.scale = Cmean.scale) %>% 
        select(APT.Cmean.scale),
      rename(s1.PDP.WIT, WIT.Cmean.scale = Cmean.scale) %>% 
        select(WIT.Cmean.scale))

ggplot(s1.Cest, aes(WIT.Cmean.scale, APT.Cmean.scale)) +
  geom_point() +
  geom_smooth(method = "lm") +
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "WIT PDP-C", y = "AP PDP-C") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(WIT.Cmean.scale ~ APT.Cmean.scale, data = s1.Cest) %>% summary()

# A estimates
s1.Aest = 
  cbind(rename(s1.PDP.APT, APT.AResid.scale = AResid.scale) %>% 
        select(APT.AResid.scale),
      rename(s1.PDP.WIT, WIT.AResid.scale = AResid.scale) %>% 
        select(WIT.AResid.scale))

ggplot(s1.Aest, aes(WIT.AResid.scale, APT.AResid.scale)) +
  geom_point() +
  geom_smooth(method = "lm") +
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "WIT PDP-A", y = "AP PDP-A") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(WIT.AResid.scale ~ APT.AResid.scale, data = s1.Aest) %>% summary()


# Compare C and A resid 
s1.Aest$EstType = "A"
names(s1.Aest) = c("APT", "WIT", "EstType")

s1.Cest$Type = "C"
names(s1.Cest) = c("APT", "WIT", "EstType")

compareAC = rbind(s1.Aest, s1.Cest)

ggplot(compareAC, aes(WIT, APT, pch = EstType)) +
  geom_point(aes(shape = EstType), size = 2.5, alpha = .7) +
  scale_shape_manual(values=c(1,17)) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme_bw() +
  geom_smooth(method = "lm", aes(linetype=EstType), color = "black", fullrange = T) +
  labs(x = "PDP estimates for WIT", y = "PDP estimates for APT") +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "cm"),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))+
  coord_cartesian(expand=c(0,0))

ggsave("./Figures/Study1_CompareAC.tiff")

lm(WIT ~ APT*EstType, data = compareAC) %>% summary()

```
``` {r, echo=F, eval=F}
# run other models to get f^2 (measures local effect size)
# f^2 = (R^2(full) - R^2(reduced))/(1-R^2(full))
# where full has all predictors/interactions and reduced has all but the one you want the effect size for

full = lm(WIT ~ APT*EstType, data = compareAC) %>% summary()
reduced = lm(WIT ~ APT+EstType, data = compareAC) %>% summary() 

(full$r.squared - reduced$r.squared)/(1-full$r.squared)

```
####Study 2:  
``` {r correl2, echo=F}
# compare PDP-C estimates across tasks
s2.PDP.APT = read.delim("Study2_pdpEstimates_APT.txt")
s2.PDP.WIT = read.delim("Study2_pdpEstimates_WIT.txt")

# take out subs with missing data
s2.PDP.APT = s2.PDP.APT[!(s2.PDP.APT$Subject %in% s2.bs.WIT$Subject) & !(s2.PDP.APT$Subject %in% s2.bs.APT$Subject),]

s2.PDP.WIT = s2.PDP.WIT[!(s2.PDP.WIT$Subject %in% s2.bs.WIT$Subject) & !(s2.PDP.WIT$Subject %in% s2.bs.APT$Subject),]

# Add standarized estimates (depends on subjects included)
s2.PDP.APT$Cmean.scale = scale(s2.PDP.APT$C_mean)
s2.PDP.WIT$Cmean.scale = scale(s2.PDP.WIT$C_mean)
s2.PDP.APT$AResid.scale = scale(s2.PDP.APT$AResid)
s2.PDP.WIT$AResid.scale = scale(s2.PDP.WIT$AResid)

## COMPARISON BETWEEN PDP ESTIMATES FROM INITIAL SUBMISSION AND CHANGED PDP ESTIMATES
s2.widePDP = read.delim("Old/Study2_PDP_wide.txt")
# APT C ESTIMATES: r = .95
cor(s2.widePDP$APT_MeanC, s2.PDP.APT$C_mean)
ggsave("./Compare new and old PDP est/Study2_APT_Cmean.jpg",
       qplot(s2.widePDP$APT_MeanC, s2.PDP.APT$C_mean,
             xlab = "Old PDP-C", ylab = "New PDP-C", main = "APT"))
# APT A ESTIMATES: r = .72
cor(s2.widePDP$APT_AResid, s2.PDP.APT$AResid)
ggsave("./Compare new and old PDP est/Study2_APT_AResid.jpg",
       qplot(s2.widePDP$APT_AResid, s2.PDP.APT$AResid,
             xlab = "Old PDP-A", ylab = "New PDP-A", main = "APT"))
# WIT C ESTIMATES: r = .98
cor(s2.widePDP$WIT_MeanC, s2.PDP.WIT$C_mean)
ggsave("./Compare new and old PDP est/Study2_WIT_Cmean.jpg",
       qplot(s2.widePDP$WIT_MeanC, s2.PDP.WIT$C_mean,
             xlab = "Old PDP-C", ylab = "New PDP-C", main = "WIT"))
# WIT A ESTIMATES: r = .77
cor(s2.widePDP$WIT_AResid, s2.PDP.WIT$AResid)
ggsave("./Compare new and old PDP est/Study2_WIT_AResid.jpg",
       qplot(s2.widePDP$WIT_AResid, s2.PDP.WIT$AResid,
             xlab = "Old PDP-A", ylab = "New PDP-A", main = "WIT"))

# C estimates
s2.Cest = 
  cbind(rename(s2.PDP.APT, APT.Cmean.scale = Cmean.scale) %>% 
        select(APT.Cmean.scale),
      rename(s2.PDP.WIT, WIT.Cmean.scale = Cmean.scale) %>% 
        select(WIT.Cmean.scale))

ggplot(s2.Cest, aes(WIT.Cmean.scale, APT.Cmean.scale)) +
  geom_point() +
  geom_smooth(method = "lm") +
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "WIT PDP-C", y = "AP PDP-C") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(WIT.Cmean.scale ~ APT.Cmean.scale, data = s2.Cest) %>% summary()

# A estimates
s2.Aest = 
  cbind(rename(s2.PDP.APT, APT.AResid.scale = AResid.scale) %>% 
        select(APT.AResid.scale),
      rename(s2.PDP.WIT, WIT.AResid.scale = AResid.scale) %>% 
        select(WIT.AResid.scale))

ggplot(s2.Aest, aes(WIT.AResid.scale, APT.AResid.scale)) +
  geom_point() +
  geom_smooth(method = "lm") +
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "WIT PDP-A", y = "AP PDP-A") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(WIT.AResid.scale ~ APT.AResid.scale, data = s2.Aest) %>% summary()


# Compare C and A resid 
s2.Aest$EstType = "A"
names(s2.Aest) = c("APT", "WIT", "EstType")

s2.Cest$Type = "C"
names(s2.Cest) = c("APT", "WIT", "EstType")

compareAC = rbind(s2.Aest, s2.Cest)

ggplot(compareAC, aes(WIT, APT, pch = EstType)) +
  geom_point(aes(shape = EstType), size = 2.5, alpha = .7) +
  scale_shape_manual(values=c(1,17)) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme_bw() +
  geom_smooth(method = "lm", aes(linetype=EstType), color = "black", fullrange = T) +
  labs(x = "PDP estimates for WIT", y = "PDP estimates for APT") +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "cm"),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))+
  coord_cartesian(expand=c(0,0))

ggsave("./Figures/Study2_CompareAC.tiff")

lm(WIT ~ APT*EstType, data = compareAC) %>% summary()

```
``` {r, echo=F, eval=F}
# run other models to get f^2 (measures local effect size)
# f^2 = (R^2(full) - R^2(reduced))/(1-R^2(full))
# where full has all predictors/interactions and reduced has all but the one you want the effect size for

full = lm(WIT ~ APT*EstType, data = compareAC) %>% summary()
reduced = lm(WIT ~ APT+EstType, data = compareAC) %>% summary() 

(full$r.squared - reduced$r.squared)/(1-full$r.squared)

```

### STOP HERE

### 4. Effect of observer on response accuracy bias, PDP-A, PDP-C, anxiety

####Study 1:  
``` {r}

WIT = select(s1.widePDP, Subject, Observer, WIT_MeanC, WIT_AResid) %>% 
  rename(MeanC = WIT_MeanC, AResid = WIT_AResid)
WIT$Task = "WIT"

APT = select(s1.widePDP, Subject, Observer, APT_MeanC, APT_AResid) %>% 
  rename(MeanC = APT_MeanC, AResid = APT_AResid)
APT$Task = "APT"

# put them together
s1.wide = rbind(WIT, APT)

# add IMS data
IMS = read.delim("Study1_experimentalTrials.txt") %>% 
  filter(blockName == "WIT", SubTrial == 1) %>% 
  select(Subject, IMS)

s1.wide$IMS = NA
for (k in IMS$Subject[!(is.na(IMS$IMS))]) {
  s1.wide$IMS[s1.wide$Subject == k] = IMS$IMS[IMS$Subject == k]
}

# add response accuracy data
s1.wide$perfBias = NA
for (k in unique(s1.perfBias$Subject)) {
  s1.wide$perfBias[s1.wide$Subject == k & s1.wide$Task == "WIT"] = s1.perfBias$WITperfBias[s1.perfBias$Subject == k]
  s1.wide$perfBias[s1.wide$Subject == k & s1.wide$Task == "APT"] = s1.perfBias$APperfBias[s1.perfBias$Subject == k]  
}



# Calculate partial etq-squared 
# SS.effect/(SS.effect + SS.total)

# Perf bias
m1 = lm(perfBias ~ scale(IMS)*Observer*Task, data = s1.wide) %>% 
  summary()
# PDP-C
m2 = lm(MeanC ~ scale(IMS)*Observer*Task, data = s1.wide) %>% 
  summary()
# PDP-A
m3 = lm(AResid ~ scale(IMS)*Observer*Task, data = s1.wide) %>% 
  summary()

```

**Perf bias:**
  
``` {r}
m1
```

**PDP-C estimates:**
  
``` {r}
m2
```

**PDP-A estimates:**
  
``` {r}
m3
```
**Probe interaction for PDP-A:**  
*Observer Present:*
```{r}
# Look at each level of observer separately
## Present
lm(AResid ~ scale(IMS)*Task, data = s1.wide[s1.wide$Observer == "Present",]) %>%
  summary()
```
*Observer Absent:*
``` {r}
## Absent
lm(AResid ~ scale(IMS)*Task, data = s1.wide[s1.wide$Observer == "Absent",]) %>%
  summary()
```
**Simple slopes:**
``` {r}
# simple slopes
lm(scale(AResid) ~ scale(IMS), data = s1.wide[s1.wide$Observer == "Present" & s1.wide$Task == "APT",]) %>%
  summary()
lm(scale(AResid) ~ scale(IMS), data = s1.wide[s1.wide$Observer == "Present" & s1.wide$Task == "WIT",]) %>%
  summary()

# Plot 3-way Observer x IMS x Task interaction on PDP-A
ggplot(s1.wide, aes(IMS, AResid, pch = Task)) +
  geom_point(aes(shape = Task), size = 2.5, alpha = .7) +
  facet_wrap(~Observer) +
  scale_shape_manual(values=c(1,17)) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme_bw() +
  geom_smooth(method = "lm", aes(linetype=Task), color = "black") +
  labs(x = "Internal motivation (IMS)", y = "PDP-Auto estimate") +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "cm"),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        strip.text.x = element_text(size = 16)) +
  coord_cartesian(ylim=c(-.5,.5))

ggsave("./Figures/3way-PDPAuto_Study1.tiff", width = 9, height = 5)


```

####Study 2:  
``` {r}
WIT = select(s2.widePDP, Subject, Observer, WIT_MeanC, WIT_AResid) %>% 
  rename(MeanC = WIT_MeanC, AResid = WIT_AResid)
WIT$Task = "WIT"

APT = select(s2.widePDP, Subject, Observer, APT_MeanC, APT_AResid) %>% 
  rename(MeanC = APT_MeanC, AResid = APT_AResid)
APT$Task = "APT"

# put them together
s2.wide = rbind(WIT, APT)


# add IMS data
IMS = read.delim("Study2_experimentalTrials.txt") %>% 
  filter(blockName == "WIT_1", SubTrial == 1) %>% 
  select(Subject, IMS)

s2.wide$IMS = NA
for (k in IMS$Subject[!(is.na(IMS$IMS))]) {
  s2.wide$IMS[s2.wide$Subject == k] = IMS$IMS[IMS$Subject == k]
}

# add response accuracy data
s2.wide$perfBias = NA
for (k in unique(s2.perfBias$Subject)) {
  s2.wide$perfBias[s2.wide$Subject == k & s2.wide$Task == "WIT"] = s2.perfBias$WITperfBias[s2.perfBias$Subject == k]
  s2.wide$perfBias[s2.wide$Subject == k & s2.wide$Task == "APT"] = s2.perfBias$APperfBias[s2.perfBias$Subject == k]  
}



# Calculate partial etq-squared for 2 way interaction
# SS.effect/(SS.effect + SS.total)

# Perf bias
m5 = lm(perfBias ~ scale(IMS)*Observer*Task, data = s2.wide) %>% 
  summary()
# PDP-C
m6 = lm(MeanC ~ scale(IMS)*Observer*Task, data = s2.wide) %>% 
  summary()
# PDP-A
m7 = lm(AResid ~ scale(IMS)*Observer*Task, data = s2.wide) %>% 
  summary()

```

**Perf bias:**
  
``` {r}
m5
```

**PDP-C estimates:**
  
``` {r}
m6
```

**PDP-A estimates:**
  
``` {r}
m7

# Plot 3-way Observer x IMS x Task interaction on PDP-A
ggplot(s2.wide, aes(IMS, AResid, pch = Task)) +
  geom_point(aes(shape = Task), size = 2.5, alpha = .7) +
  facet_wrap(~Observer) +
  scale_shape_manual(values=c(1,17)) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme_bw() +
  geom_smooth(method = "lm", aes(linetype=Task), color = "black") +
  labs(x = "Internal motivation (IMS)", y = "PDP-Auto estimate") +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "cm"),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        strip.text.x = element_text(size = 16)) +
  coord_cartesian(ylim=c(-.5,.5))

ggsave("./Figures/3way-PDPAuto_Study2.tiff", width = 9, height = 5)

```



