---
title: Observer analyses
author: Hannah, 9/19/2018
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(width=140)
require(dplyr)
require(tidyr)
require(ggplot2)
require(lme4)
require(lmerTest)
require(knitr)
require(reshape2)
```

Data for Study 1 was collected in Fall 2015. Data for Study 2 was collected in Fall 2016.

**In Study 1:**  
- 101 subjects participated  
- 8 subjects' AP data was discarded (see "Study1_badsubsAP.txt")  
- 9 subjects' WIT data was discarded (see "Study1_badsubsWIT.txt")    
*This left 93 subjects with AP data and 92 subjects with WIT data.*

Additionally, IMS/EMS data is missing for subs 3, 27, 53, 82, 88, 89, 90, and 101. 

**In Study 2:**  
- 206 subjects participated  
- 8 subjects' AP data was discarded (see "Study2_badsubsAP.txt")  
- 7 subjects' WIT data was discarded (see "Study2_badsubsWIT.txt")  
*This left 198 subjects with AP data and 199 subjects with WIT data.*

Additionally, IMS/EMS data is missing for 111, 189, and 201.

There were 48 trials for each condition in each task. In Study 2, each task was split into two sections so that participants could answer anxiety questions in the middle and end of each task.

### 1. Accuracy in each task:  
#### 2 (Prime: Black/White) x 2 (Target: gun/tool or positive/negative) rANOVA  
Only showing interaction indicating racial bias (Prime x Target). For calculation of effect sizes, see "7 Effect sizes.R"  
#### Study 1:  
**WIT**  
```{r data, echo = FALSE}
# For analyses with accuracy as DV, need trials to be grouped into conditions (ie number of errors in each condition)
s1.acc = read.delim("Study1_errCountLong.txt")

# separate by task
s1.acc.AP = s1.acc[s1.acc$Task == "AP",]
s1.acc.WIT = s1.acc[s1.acc$Task == "WIT",]

s1.acc.AP$TargetType = factor(s1.acc.AP$TargetType)
s1.acc.WIT$TargetType = factor(s1.acc.WIT$TargetType)
s1.acc.AP$Subject = factor(s1.acc.AP$Subject)
s1.acc.WIT$Subject = factor(s1.acc.WIT$Subject)

# Race x Valence on accuracy (WIT)
sum = aov(numErr ~ PrimeType*TargetType + Error(Subject/(PrimeType*TargetType)), data = s1.acc.WIT) %>% 
  summary()

sum$`Error: Subject:PrimeType:TargetType`


```

**AP**
``` {r AP, echo = FALSE}
# Race x Valence on accuracy (WIT)
sum = aov(numErr ~ PrimeType*TargetType + Error(Subject/(PrimeType*TargetType)), data = s1.acc.AP) %>% 
  summary()

sum$`Error: Subject:PrimeType:TargetType`
```


#### Study 2: 
Only showing interaction indicating racial bias (Prime x Target). For calculation of effect sizes, see "7 Effect sizes.R"  
**WIT**  
```{r data2, echo = FALSE}
# For analyses with accuracy as DV, need trials to be grouped into conditions (ie number of errors in each condition)
s2.acc = read.delim("Study2_errCountLong.txt")

# separate by task
s2.acc.AP = s2.acc[s2.acc$Task == "AP",]
s2.acc.WIT = s2.acc[s2.acc$Task == "WIT",]

s2.acc.AP$TargetType = factor(s2.acc.AP$TargetType)
s2.acc.WIT$TargetType = factor(s2.acc.WIT$TargetType)
s2.acc.AP$Subject = factor(s2.acc.AP$Subject)
s2.acc.WIT$Subject = factor(s2.acc.WIT$Subject)

# Race x Valence on accuracy (WIT)
sum = aov(numErr ~ PrimeType*TargetType + Error(Subject/(PrimeType*TargetType)), data = s2.acc.WIT) %>% 
  summary()

sum$`Error: Subject:PrimeType:TargetType`
```

**AP**
``` {r AP2, echo = FALSE}
# Race x Valence on accuracy (WIT)
sum = aov(numErr ~ PrimeType*TargetType + Error(Subject/(PrimeType*TargetType)), data = s2.acc.AP) %>% 
  summary()

sum$`Error: Subject:PrimeType:TargetType`
```

### 2. Comparing accuracy across tasks

#### Study 1
Excludes subjects that don't have data in both tasks (only includes sample of 90).  

#### A. Correlation between performance bias scores on each task
``` {r perfBias.s1, echo=F, warning=F}
s1.perfBias = read.delim("Study1_perfBias.txt")

# Look at correlation between tasks
ggplot(s1.perfBias, aes(APStand, WITStand)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "Stand. Performance bias on AP", y = "Stand. Performance bias on WIT") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(APStand ~ WITStand, data = s1.perfBias) %>%
  summary()
```

#### B. Examine 3 way Prime x Target x Task interaction  
``` {r 3way.s1, echo=F, wanring=F}
# Look just at subjects that have data for both tasks, otherwise throws error ("Error() model is singular")
# Probably because some subjects don't have data across both levels of task
s1.bsWIT = read.delim("Study1_badsubsWIT.txt")
s1.bsAP = read.delim("Study1_badsubsAP.txt")
s1.acc.nobs = s1.acc[!(s1.acc$Subject %in% s1.bsWIT$Subject) & !(s1.acc$Subject %in% s1.bsAP$Subject),]
s1.acc.nobs$Subject = factor(s1.acc.nobs$Subject)

# Total number of errors (looking at three-way interaction)
facet_labels <- c(AP = "APT", WIT = "WIT")

# Figure 1 ----------------------------------------------------------------
ggplot(s1.acc.nobs, aes(PrimeType, (48-numErr)/48, fill = ConType)) +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .2) +
  facet_wrap(~Task, labeller=labeller(Task = facet_labels)) + 
  #  ggtitle("Total number of errors") +
  labs(y = "Accuracy rate", x = "Race of Prime") +
  scale_fill_manual(values=c("black","grey70"), guide = guide_legend(title = NULL)) +
  theme_bw() +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        strip.text.x = element_text(face = "bold", size = 14),
        strip.background = element_rect(fill = "grey98"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

ggsave("./Figures/Accuracy_Study1.tiff")


# See if pattern of racial bias differs across two tasks- TOTAL ERRORS
sum2 = aov(numErr ~ (PrimeType*ConType*Task)+Error(Subject/(PrimeType*ConType*Task)), data = s1.acc.nobs) %>%
  summary()

sum2$`Error: Subject:PrimeType:ConType:Task`

```

``` {r, echo = F, eval=F}
# check correlation between conditions for sensitivity power analysis
wide = spread(select(s1.acc.nobs, Subject, TrialType, numErr), TrialType, numErr)

rs = cor(select(wide, -Subject))
```

#### Study 2
Excludes subjects that don't have data in both tasks (only includes sample of 195).  

#### A. Correlation between performance bias scores on each task
``` {r perfBias.s2, echo=F, warning=F}
s2.perfBias = read.delim("Study2_perfBias.txt")

# Look at correlation between tasks
ggplot(s2.perfBias, aes(APStand, WITStand)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "Stand. Performance bias on AP", y = "Stand. Performance bias on WIT") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(APStand ~ WITStand, data = s2.perfBias) %>%
  summary()
```

#### B. Examine 3 way Prime x Target x Task interaction  
``` {r 3way.s2, echo=F, wanring=F}
# Look just at subjects that have data for both tasks, otherwise throws error ("Error() model is singular")
# Probably because some subjects don't have data across both levels of task
s2.bsWIT = read.delim("Study2_badsubsWIT.txt")
s2.bsAP = read.delim("Study2_badsubsAP.txt")
s2.acc.nobs = s2.acc[!(s2.acc$Subject %in% s2.bsWIT$Subject) & !(s2.acc$Subject %in% s2.bsAP$Subject),]
s2.acc.nobs$Subject = factor(s2.acc.nobs$Subject)

# Total number of errors (looking at three-way interaction)
facet_labels <- c(AP = "APT", WIT = "WIT")

# Figure 1 ----------------------------------------------------------------
ggplot(s2.acc.nobs, aes(PrimeType, (48-numErr)/48, fill = ConType)) +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .2) +
  facet_wrap(~Task, labeller=labeller(Task = facet_labels)) + 
  #  ggtitle("Total number of errors") +
  labs(y = "Accuracy rate", x = "Race of Prime") +
  scale_fill_manual(values=c("black","grey70"), guide = guide_legend(title = NULL)) +
  theme_bw() +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        strip.text.x = element_text(face = "bold", size = 14),
        strip.background = element_rect(fill = "grey98"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

ggsave("./Figures/Accuracy_Study2.tiff")


# See if pattern of racial bias differs across two tasks- TOTAL ERRORS
sum2 = aov(numErr ~ (PrimeType*ConType*Task)+Error(Subject/(PrimeType*ConType*Task)), data = s2.acc.nobs) %>%
  summary()

sum2$`Error: Subject:PrimeType:ConType:Task`

```

### 3. Correspondance in PDP estimates across tasks

####Study 1:  
``` {r correl, echo=F}
# compare PDP-C estimates across tasks
s1.widePDP = read.delim("Study1_PDP_wide.txt")

# C estimates
ggplot(s1.widePDP, aes(WIT_MeanC.stand, AP_MeanC.stand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "WIT PDP-C", y = "AP PDP-C") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(WIT_MeanC.stand ~ AP_MeanC.stand, data = s1.widePDP) %>% summary()

# A estimates
ggplot(s1.widePDP, aes(WIT_AResid.stand, AP_AResid.stand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "WIT PDP-A", y = "AP PDP-A") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(WIT_AResid.stand ~ AP_AResid.stand, data = s1.widePDP) %>% summary()

# Compare C and A resid 
tempC = select(s1.widePDP, Subject, WIT_MeanC.stand, AP_MeanC.stand) %>% 
  rename(WITestimate = WIT_MeanC.stand, APTestimate = AP_MeanC.stand)
tempC$Type = "PDP-C"

tempA = select(s1.widePDP, Subject, WIT_AResid.stand, AP_AResid.stand) %>% 
  rename(WITestimate = WIT_AResid.stand, APTestimate = AP_AResid.stand)
tempA$Type = "PDP-A"

compareAC = rbind(tempC, tempA)
compareAC$Type = factor(compareAC$Type)

ggplot(compareAC, aes(WITestimate, APTestimate, pch = Type)) +
  geom_point(aes(shape = Type), size = 2.5, alpha = .7) +
  scale_shape_manual(values=c(1,17)) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme_bw() +
  geom_smooth(method = "lm", aes(linetype=Type), color = "black") +
  labs(x = "PDP estimates for WIT", y = "PDP estimates for APT") +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "cm"),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))+
  coord_cartesian(ylim=c(-2.5,3), xlim=c(-2.5,3))

ggsave("./Figures/CompareAC_Study1.tiff")

lm(WITestimate ~ APTestimate*Type, data = compareAC) %>% summary()

```
``` {r, echo=F, eval=F}
# run other models to get f^2 (measures local effect size)
# f^2 = (R^2(full) - R^2(reduced))/(1-R^2(full))
# where full has all predictors/interactions and reduced has all but the one you want the effect size for

full = lm(WITestimate ~ APTestimate*Type, data = compareAC) %>% summary()
reduced = lm(WITestimate ~ APTestimate+Type, data = compareAC) %>% summary() 

(full$r.squared - reduced$r.squared)/(1-full$r.squared)

```
####Study 2:  
``` {r correl2, echo=F}
# compare PDP-C estimates across tasks
s2.widePDP = read.delim("Study2_PDP_wide.txt")

# C estimates
ggplot(s2.widePDP, aes(WIT_MeanC.stand, AP_MeanC.stand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "WIT PDP-C", y = "AP PDP-C") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(WIT_MeanC.stand ~ AP_MeanC.stand, data = s2.widePDP) %>% summary()

# A estimates
ggplot(s2.widePDP, aes(WIT_AResid.stand, AP_AResid.stand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  #  ggtitle("Correlation between accuracy on WIT and accuracy on AP") +
  labs(x = "WIT PDP-A", y = "AP PDP-A") +
  theme_bw()+
  theme(axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        title = element_text(size=20)
        #axis.text.x  = element_text(angle=90, vjust=0.5, size=16)
  )

lm(WIT_AResid.stand ~ AP_AResid.stand, data = s2.widePDP) %>% summary()

# Compare C and A resid 
tempC = select(s2.widePDP, Subject, WIT_MeanC.stand, AP_MeanC.stand) %>% 
  rename(WITestimate = WIT_MeanC.stand, APTestimate = AP_MeanC.stand)
tempC$Type = "PDP-C"

tempA = select(s2.widePDP, Subject, WIT_AResid.stand, AP_AResid.stand) %>% 
  rename(WITestimate = WIT_AResid.stand, APTestimate = AP_AResid.stand)
tempA$Type = "PDP-A"

compareAC = rbind(tempC, tempA)
compareAC$Type = factor(compareAC$Type)

ggplot(compareAC, aes(WITestimate, APTestimate, pch = Type)) +
  geom_point(aes(shape = Type), size = 2.5, alpha = .7) +
  scale_shape_manual(values=c(1,17)) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme_bw() +
  geom_smooth(method = "lm", aes(linetype=Type), color = "black") +
  labs(x = "PDP estimates for WIT", y = "PDP estimates for APT") +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "cm"),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16)) +
  coord_cartesian(ylim=c(-2.5,3), xlim=c(-2.5,3))

ggsave("./Figures/CompareAC_Study2.tiff")

lm(WITestimate ~ APTestimate*Type, data = compareAC) %>% summary()
```
``` {r, echo=F, eval=F}
# run other models to get f^2 (measures local effect size)
# f^2 = (R^2(full) - R^2(reduced))/(1-R^2(full))
# where full has all predictors/interactions and reduced has all but the one you want the effect size for

full = lm(WITestimate ~ APTestimate*Type, data = compareAC) %>% summary()
reduced = lm(WITestimate ~ APTestimate+Type, data = compareAC) %>% summary() 

(full$r.squared - reduced$r.squared)/(1-full$r.squared)

```


### 4. Effect of observer on response accuracy bias, PDP-A, PDP-C, anxiety

####Study 1:  
``` {r}

WIT = select(s1.widePDP, Subject, Observer, WIT_MeanC, WIT_AResid) %>% 
  rename(MeanC = WIT_MeanC, AResid = WIT_AResid)
WIT$Task = "WIT"

APT = select(s1.widePDP, Subject, Observer, APT_MeanC, APT_AResid) %>% 
  rename(MeanC = APT_MeanC, AResid = APT_AResid)
APT$Task = "APT"

# put them together
s1.wide = rbind(WIT, APT)

# add IMS data
IMS = read.delim("Study1_experimentalTrials.txt") %>% 
  filter(blockName == "WIT", SubTrial == 1) %>% 
  select(Subject, IMS)

s1.wide$IMS = NA
for (k in IMS$Subject[!(is.na(IMS$IMS))]) {
  s1.wide$IMS[s1.wide$Subject == k] = IMS$IMS[IMS$Subject == k]
}

# add response accuracy data
s1.wide$perfBias = NA
for (k in unique(s1.perfBias$Subject)) {
  s1.wide$perfBias[s1.wide$Subject == k & s1.wide$Task == "WIT"] = s1.perfBias$WITperfBias[s1.perfBias$Subject == k]
  s1.wide$perfBias[s1.wide$Subject == k & s1.wide$Task == "APT"] = s1.perfBias$APperfBias[s1.perfBias$Subject == k]  
}



# Calculate partial etq-squared 
# SS.effect/(SS.effect + SS.total)

# Perf bias
m1 = lm(perfBias ~ scale(IMS)*Observer*Task, data = s1.wide) %>% 
  summary()
# PDP-C
m2 = lm(MeanC ~ scale(IMS)*Observer*Task, data = s1.wide) %>% 
  summary()
# PDP-A
m3 = lm(AResid ~ scale(IMS)*Observer*Task, data = s1.wide) %>% 
  summary()

```

**Perf bias:**
  
``` {r}
m1
```

**PDP-C estimates:**
  
``` {r}
m2
```

**PDP-A estimates:**
  
``` {r}
m3
```
**Probe interaction for PDP-A:**  
*Observer Present:*
```{r}
# Look at each level of observer separately
## Present
lm(AResid ~ scale(IMS)*Task, data = s1.wide[s1.wide$Observer == "Present",]) %>%
  summary()
```
*Observer Absent:*
``` {r}
## Absent
lm(AResid ~ scale(IMS)*Task, data = s1.wide[s1.wide$Observer == "Absent",]) %>%
  summary()
```
**Simple slopes:**
``` {r}
# simple slopes
lm(scale(AResid) ~ scale(IMS), data = s1.wide[s1.wide$Observer == "Present" & s1.wide$Task == "APT",]) %>%
  summary()
lm(scale(AResid) ~ scale(IMS), data = s1.wide[s1.wide$Observer == "Present" & s1.wide$Task == "WIT",]) %>%
  summary()

# Plot 3-way Observer x IMS x Task interaction on PDP-A
ggplot(s1.wide, aes(IMS, AResid, pch = Task)) +
  geom_point(aes(shape = Task), size = 2.5, alpha = .7) +
  facet_wrap(~Observer) +
  scale_shape_manual(values=c(1,17)) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme_bw() +
  geom_smooth(method = "lm", aes(linetype=Task), color = "black") +
  labs(x = "Internal motivation (IMS)", y = "PDP-Auto estimate") +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "cm"),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        strip.text.x = element_text(size = 16)) +
  coord_cartesian(ylim=c(-.5,.5))

ggsave("./Figures/3way-PDPAuto_Study1.tiff", width = 9, height = 5)


```

####Study 2:  
``` {r}
WIT = select(s2.widePDP, Subject, Observer, WIT_MeanC, WIT_AResid) %>% 
  rename(MeanC = WIT_MeanC, AResid = WIT_AResid)
WIT$Task = "WIT"

APT = select(s2.widePDP, Subject, Observer, APT_MeanC, APT_AResid) %>% 
  rename(MeanC = APT_MeanC, AResid = APT_AResid)
APT$Task = "APT"

# put them together
s2.wide = rbind(WIT, APT)


# add IMS data
IMS = read.delim("Study2_experimentalTrials.txt") %>% 
  filter(blockName == "WIT_1", SubTrial == 1) %>% 
  select(Subject, IMS)

s2.wide$IMS = NA
for (k in IMS$Subject[!(is.na(IMS$IMS))]) {
  s2.wide$IMS[s2.wide$Subject == k] = IMS$IMS[IMS$Subject == k]
}

# add response accuracy data
s2.wide$perfBias = NA
for (k in unique(s2.perfBias$Subject)) {
  s2.wide$perfBias[s2.wide$Subject == k & s2.wide$Task == "WIT"] = s2.perfBias$WITperfBias[s2.perfBias$Subject == k]
  s2.wide$perfBias[s2.wide$Subject == k & s2.wide$Task == "APT"] = s2.perfBias$APperfBias[s2.perfBias$Subject == k]  
}



# Calculate partial etq-squared for 2 way interaction
# SS.effect/(SS.effect + SS.total)

# Perf bias
m5 = lm(perfBias ~ scale(IMS)*Observer*Task, data = s2.wide) %>% 
  summary()
# PDP-C
m6 = lm(MeanC ~ scale(IMS)*Observer*Task, data = s2.wide) %>% 
  summary()
# PDP-A
m7 = lm(AResid ~ scale(IMS)*Observer*Task, data = s2.wide) %>% 
  summary()

```

**Perf bias:**
  
``` {r}
m5
```

**PDP-C estimates:**
  
``` {r}
m6
```

**PDP-A estimates:**
  
``` {r}
m7

# Plot 3-way Observer x IMS x Task interaction on PDP-A
ggplot(s2.wide, aes(IMS, AResid, pch = Task)) +
  geom_point(aes(shape = Task), size = 2.5, alpha = .7) +
  facet_wrap(~Observer) +
  scale_shape_manual(values=c(1,17)) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme_bw() +
  geom_smooth(method = "lm", aes(linetype=Task), color = "black") +
  labs(x = "Internal motivation (IMS)", y = "PDP-Auto estimate") +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "cm"),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        strip.text.x = element_text(size = 16)) +
  coord_cartesian(ylim=c(-.5,.5))

ggsave("./Figures/3way-PDPAuto_Study2.tiff", width = 9, height = 5)

```



